Declarative runtime reconfiguration of pulverised distributed systems \thanks{Identify applicable funding agency here. If none, delete this.}

### 2023-05-11 paper-2023-acsos-pulverization.tex
Add initial description of the small case study

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{listings}
\usepackage{listing-style}
\usepackage[hidelinks]{hyperref}

@@

\subsection{Small scale: crowd alert}

>>>>

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{listings}
\usepackage{listing-style}
\usepackage[hidelinks]{hyperref}
\usepackage{svg}

@@

\subsection{Small scale: crowd alert}
\label{sec:small-scale-crowd-alert}

In this section we present a simple scenario where the pulverization framework is used to implement a crowd alert system:
we simulate a laboratory where a safety system warns people when they are too close to each other.
%
Each person is equipped with a wearable device that is able to detect the distance from other devices and send the distances data to the
alert system.
%
The people in the laboratory must observe a safety distance, and the system warns them when the distance is not respected by showing a red light
when they are too close to each other, and a green color when the distance is respected (see~\Cref{fig:crowd-alert}).
%
\begin{figure*}[ht]
    \centering
    \includesvg[width=.8\textwidth]{figures/crow-laboratory-demo.drawio.svg}
    \caption{
        Representation of the scenario described in the~\Cref{sec:small-scale-crowd-alert}
        where more the people are far from each other, more the color of the screen is green.
        More the people are close to each other, more the color of the screen is red.
        The blue dot represents the wearable device and the link between the devices represents the distance between them.
        The rectangle represents the monitor in the laboratory which shows the congestion level of the laboratory (via the color described above).
    }
    \label{fig:crowd-alert}
\end{figure*}
%
The system is composed of two kind of devices: \emph{wearable} and \emph{laboratory}.
%
The former represents the wearable devices that is worn by the people, and consists of the following pulverized components:
$\beta$, $\chi$, and $\sigma$.
%
The \emph{behaviour} ($\beta$) component is responsible for converting the raw data from the sensor into the distance
between the device and the others; the \emph{sensors} ($\sigma$) component is responsible for perceiving the other devices and
the \emph{communication} ($\chi$) component is responsible for sending the data to the alert system.
%
The latter represents the alert system and consists of the following pulverized components:
$\beta$, $\kappa$, $\chi$, and $\alpha$.
%
The \emph{behaviour} ($\beta$) component is responsible for evaluating the meand distance between the devices,
the \emph{actuators} ($\alpha$) is responsible for triggering the alarm showing a color in the screen,
and the \emph{communication} ($\chi$) component is responsible for receiving the data from the wearable devices.

The infrastructure defined for this scenario is described as follow:

\begin{itemize}
    \item \emph{Smartphones} are the devices used by the people to detect the distance from the others;
    \item \emph{Local PC} is the device used to show the alarm in the laboratory;
    \item \emph{Server} is the device used run the crowd algorithm and the wearable logic. 
\end{itemize}

The initial deployment of the system starts with the $\beta_{werable}$ executed in the \emph{Server},
the $\sigma_{wearable}$ and $\chi_{werable}$ executed in the \emph{Smartphones},
and all the \emph{Laboratory} components are executed in the \emph{Local PC}.
%
Given the infrastracture defined above, we simulate also a condition where the \emph{Server} is overloaded and, via pulverization,
we reconfigure the execution of all the $\beta_{werable}$ component to the \emph{Smartphone}.
%
